Depression and suicidality as costly signals of need

### 2021-04-29 Paper.rmd
Minor intro change

As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of conflict or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals. When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].

>>>>

As they are prohibitively costly for those in minor need, the costs of depression and suicidal behavior may be particularly important in times of substantial conflicts of interest or when the level of support needed to address one's situation is substantial, both of which should be expected to increase the payoff of manipulating others through fake signals. When either condition applies, less costly signals like verbal requests, facial sadness, and crying are likely to be less reliable as their low costs can easily be made up for with increased social support, thereby favoring the use of costlier signals so long as the costs of signaling are outweighed by the benefits [@SymeHagen2021].
